
\documentclass[titlepage]{article}

\begin{document}


\subsection{Determining Crustal Structure}

From the timing of the reverberations, the bulk properties of the crust can be determined. There is of course a tradeoff between thickness of the crust and the velocity of the crust. However, each of the reverberations has a different tradeoff, and hence by analyzing all three phases the correct depth and velocity can be determined.

However, it has been shown ****[REF]*** that the timing of the reverberations is largely insensitive to absolute P and S velocities in the layer, and the best that can be done is to extract the ration of the P to S wave velocity. Therefore a P velocity is usually assumed, and the best combination of crustal thickness and ratio of P to S wave velocity is calculated.

The relative arrival times of the three reverberations with respect to the direct P wave are given by:

$t_{Ps} - t_{P} = H ( \eta_\beta - \eta_\alpha )$

$t_{PpPs} - t_{P} = H ( \eta_\beta + \eta_\alpha )$

$t_{PsPs/PpSs} - t_{P} = 2 H \eta_\beta$

where $\eta_\alpha = \sqrt{1/V_P^2 - p^2}$ and $\eta_\beta = \sqrt{1/V_S^2 - p^2}$ represent the P and S wave vertical slowness respectively.

If the receiver functions are of high quality, then it is possible to simply pick the arrival times of the reverberations and find a best fit of crustal properties. Many studies have done exactly this, ***REF Zandt and Ammon***. However, in making use of noisier stations atop complex structure recording smaller earthquakes, it can be difficult if not impossible to descern these arrivals by eye. In this case, looking at receiver functions from many events at a given station is desirable, which leads to use of a stacking technique.

The simplest stacking technique is to sum the receiver functions. Unless the events are all at similar distances, this is unlikely to generate good results as the timing of the reverberations has a dependence on the ray parameter, which depends on the distance. A slant stack can be used to account for the ray parameter dependence. A further stacking idea to remove the ray parameter dependence is to transform the receiver function, as amplitude as a function of time, to a H\Kappa plot, with amplitude as a function of thickness, H, and $\Kappa = V_p/V_s$. Once this transformation is done, there is no longer a ray parameter dependence, and H\Kappa plots from events at many distances can be summed.


\end{document}